Extracting The Power of Dependent Types

### 2021-07-14 paper.tex
Add some missing citations

One powerful method for enforcing almost any functional property
of a program statically is by using \emph{dependent types}.
In a dependently typed language, properties can be encoded as types,
and if the program typechecks, the property is guaranteed to hold.
If we can extend our existing language with dependent types
(for verification part) and then eliminate them (for using the original
compiler), then our goal is achieved.

@@

Meanwhile, a deep embedding defines a data type to represent the AST
of the embedded language.  This requires us to define a type system
and evaluator for the language separately.  With a dependently typed
host language the AST and the type system can be defined as a single
data structure, which is typically referred to as a tagless
interpreter~\cite{}.  The benefit of deep embedding is that we get
full access to the syntactic structure of the embedded program.  This
approach works beautifully for embedded languages with simple type
systems. However, for embedded languages with dependent types,
tagless interpreters are technically possible~\cite{}, but
are extremely challenging to define and use in practice.

>>>>

One powerful method for enforcing almost any functional property of a
program statically is by using \emph{dependent types}, as used for
example in Coq~\cite{Coq-8-13-2} or Agda~\cite{agda-2-6-2}.  In a
dependently typed language, properties can be encoded as types, and if
the program typechecks, the property is guaranteed to hold.  If we can
extend our existing language with dependent types (for verification
part) and then eliminate them (for using the original compiler), then
our goal is achieved.

@@

Meanwhile, a deep embedding defines a data type to represent the AST
of the embedded language.  This requires us to define a type system
and evaluator for the language separately.  With a dependently typed
host language the AST and the type system can be defined as a single
data structure, which is typically referred to as a tagless
interpreter~\citep{PasalicTS02}.  The benefit of deep embedding is that we get
full access to the syntactic structure of the embedded program.  This
approach works beautifully for embedded languages with simple type
systems. However, for embedded languages with dependent types, tagless
interpreters are technically
possible~\citep{CHAPMAN200921,10.1007/978-3-540-74464-1_7}, but are
extremely challenging to define and use in practice.
